MyTitle

### 2024-10-30 paper/main.tex
updated

By choosing $\Pbb$ appropriately, we can construct $M[G]$ with various properties.
What holds or does not hold in $M[G]$ can be identified using the forcing relation.
The forcing relation is defined recursively on formulas in a forcing language.
The forcing language is an extension of tha language of set theory by adding the elements of $M^{\Pbb}$ as constants.
\begin{dfn} %kunen
  We define the \emph{forcing relation} $\Vdash$ for formulas in the forcing language and $p \in \Pbb$ recursively
  \footnote{Specifically}
  as follows:
  \begin{enumerate}
    \item $p \Vdash \dot{x} = \dot{y} \Leftrightarrow \forall \dot{z} \in \text{dom}(\dot{x}) \cup \text{dom}(\dot{y})\,
\forall q \leq_{\Pbb} p \, (q \Vdash \dot{z} \in \dot{x} \leftrightarrow q \Vdash \dot{z} \in \dot{y})$
    \item $p \Vdash \dot{x} \in \dot{y} \Leftrightarrow \forall q \leq_{\Pbb} p\, \exists r \leq_{\Pbb} q \, 
    \exists s \in \Pbb \, \exists \dot{z} \in M^{\Pbb} \, (\langle \dot{z}, s \rangle \in \dot{y} \land r \leq_{\Pbb} s \land r \Vdash \dot{x} = \dot{z} )$
    \item $p \Vdash \phi \land \psi \Leftrightarrow p \Vdash \phi \land p \Vdash \psi$
    \item $p \Vdash \neg \phi \Leftrightarrow \forall q \leq_{\Pbb} p \, \neg (q \Vdash \phi)$
    \item $p \Vdash \exists x \phi(x) \Leftrightarrow \forall q \leq_{\Pbb} p \, \exists r \leq_{\Pbb} q \, \exists \dot{x} \in M^{\Pbb} \, (r \Vdash \phi(\dot{x}))$
  \end{enumerate}
\end{dfn}

>>>>

By choosing $\Pbb$ appropriately, we can construct $M[G]$ with various properties.
What holds or does not hold in $M[G]$ can be identified using the forcing relation.
The forcing relation is defined recursively on formulas in a forcing language.
The forcing language is an extension of tha language of set theory by adding the elements of $M^{\Pbb}$ as constants.
\begin{dfn} %kunen
  We define the \emph{forcing relation} $\Vdash$ for formulas in the forcing language and $p \in \Pbb$ inductively
  \footnote{
    Specifically, the forcing relation is first defined for atomic formulas, and then for other formulas using structual induction. 
    Thr

  }
  as follows:
  \begin{enumerate}
    \item $p \Vdash \dot{x} = \dot{y} \Leftrightarrow \forall \dot{z} \in \text{dom}(\dot{x}) \cup \text{dom}(\dot{y})\,
\forall q \leq_{\Pbb} p \, (q \Vdash \dot{z} \in \dot{x} \leftrightarrow q \Vdash \dot{z} \in \dot{y})$
    \item $p \Vdash \dot{x} \in \dot{y} \Leftrightarrow \forall q \leq_{\Pbb} p\, \exists r \leq_{\Pbb} q \, 
    \exists s \in \Pbb \, \exists \dot{z} \in M^{\Pbb} \, (\langle \dot{z}, s \rangle \in \dot{y} \land r \leq_{\Pbb} s \land r \Vdash \dot{x} = \dot{z} )$
    \item $p \Vdash \phi \land \psi \Leftrightarrow p \Vdash \phi \land p \Vdash \psi$
    \item $p \Vdash \neg \phi \Leftrightarrow \forall q \leq_{\Pbb} p \, \neg (q \Vdash \phi)$
    \item $p \Vdash \exists x \phi(x) \Leftrightarrow \forall q \leq_{\Pbb} p \, \exists r \leq_{\Pbb} q \, \exists \dot{x} \in M^{\Pbb} \, (r \Vdash \phi(\dot{x}))$
  \end{enumerate}
\end{dfn}
